---
title: "ProBook (Windows laptop 64 bit)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
device <- 1 # Change also the title of this script.
bin_width <- 5 # ms
if (device == 1){
  dat <- read.csv('Study1_ProBook.csv', header = F)
  xRange_20ms <- seq(0, 80, bin_width)
  xRange_50ms <- seq(0, 140, bin_width)
  xRange_150ms <- seq(120, 260, bin_width)
  xRange_500ms <- seq(460, 600, bin_width)
} else if (device == 2) {
  dat <- read.csv('Study1_OptiPlex.csv', header = F)
  xRange_20ms <- seq(20, 100, bin_width)
  xRange_50ms <- seq(20, 120, bin_width)
  xRange_150ms <- seq(120, 220, bin_width)
  xRange_500ms <- seq(500, 580, bin_width)
} else if (device == 3) {
  dat <- read.csv('Study1_MacBookPro.csv', header = F)
  xRange_20ms <- seq(0, 80, bin_width)
  xRange_50ms <- seq(20, 80, bin_width)
  xRange_150ms <- seq(120, 200, bin_width)
  xRange_500ms <- seq(460, 560, bin_width)
} else {
  dat <- read.csv('Study1_iMac.csv', header = F)
  xRange_20ms <- seq(0, 80, bin_width)
  xRange_50ms <- seq(20, 100, bin_width)
  xRange_150ms <- seq(120, 200, bin_width)
  xRange_500ms <- seq(480, 560, bin_width)
}

myColNames <- c(
	"chrome_no_plugin_opto2_onset", "chrome_no_plugin_opto2_offset", "chrome_no_plugin_opto2_duration",
	"chrome_no_plugin_opto1_onset", "chrome_no_plugin_opto1_offset", "chrome_no_plugin_opto1_duration",
	"chrome_plugin_opto2_onset", "chrome_plugin_opto2_offset", "chrome_plugin_opto2_duration",
	"chrome_plugin_opto1_onset", "chrome_plugin_opto1_offset", "chrome_plugin_opto1_duration",
	"firefox_no_plugin_opto2_onset", "firefox_no_plugin_opto2_offset", "firefox_no_plugin_opto2_duration",
	"firefox_no_plugin_opto1_onset", "firefox_no_plugin_opto1_offset", "firefox_no_plugin_opto1_duration",
	"firefox_plugin_opto2_onset", "firefox_plugin_opto2_offset", "firefox_plugin_opto2_duration",
	"firefox_plugin_opto1_onset", "firefox_plugin_opto1_offset", "firefox_plugin_opto1_duration",
	"edge_no_plugin_opto2_onset", "edge_no_plugin_opto2_offset", "edge_no_plugin_opto2_duration",
	"edge_no_plugin_opto1_onset", "edge_no_plugin_opto1_offset", "edge_no_plugin_opto1_duration",
	"edge_plugin_opto2_onset", "edge_plugin_opto2_offset", "edge_plugin_opto2_duration",
	"edge_plugin_opto1_onset", "edge_plugin_opto1_offset", "edge_plugin_opto1_duration")
colnames(dat) <- myColNames

##############
# No plugin
chrome_no_plugin_20ms <- dat$chrome_no_plugin_opto2_onset[1:100] - dat$chrome_no_plugin_opto1_onset[1:100]
chrome_no_plugin_50ms <- dat$chrome_no_plugin_opto2_onset[101:200] - dat$chrome_no_plugin_opto1_onset[101:200]
chrome_no_plugin_150ms <- dat$chrome_no_plugin_opto2_onset[201:300] - dat$chrome_no_plugin_opto1_onset[201:300]
chrome_no_plugin_500ms <- dat$chrome_no_plugin_opto2_onset[301:400] - dat$chrome_no_plugin_opto1_onset[301:400]

firefox_no_plugin_20ms <- dat$firefox_no_plugin_opto2_onset[1:100] - dat$firefox_no_plugin_opto1_onset[1:100]
firefox_no_plugin_50ms <- dat$firefox_no_plugin_opto2_onset[101:200] - dat$firefox_no_plugin_opto1_onset[101:200]
firefox_no_plugin_150ms <- dat$firefox_no_plugin_opto2_onset[201:300] - dat$firefox_no_plugin_opto1_onset[201:300]
firefox_no_plugin_500ms <- dat$firefox_no_plugin_opto2_onset[301:400] - dat$firefox_no_plugin_opto1_onset[301:400]

edge_no_plugin_20ms <- dat$edge_no_plugin_opto2_onset[1:100] - dat$edge_no_plugin_opto1_onset[1:100]
edge_no_plugin_50ms <- dat$edge_no_plugin_opto2_onset[101:200] - dat$edge_no_plugin_opto1_onset[101:200]
edge_no_plugin_150ms <- dat$edge_no_plugin_opto2_onset[201:300] - dat$edge_no_plugin_opto1_onset[201:300]
edge_no_plugin_500ms <- dat$edge_no_plugin_opto2_onset[301:400] - dat$edge_no_plugin_opto1_onset[301:400]

##############
# Plugin
chrome_plugin_20ms <- dat$chrome_plugin_opto2_onset[1:100] - dat$chrome_plugin_opto1_onset[1:100]
chrome_plugin_50ms <- dat$chrome_plugin_opto2_onset[101:200] - dat$chrome_plugin_opto1_onset[101:200]
chrome_plugin_150ms <- dat$chrome_plugin_opto2_onset[201:300] - dat$chrome_plugin_opto1_onset[201:300]
chrome_plugin_500ms <- dat$chrome_plugin_opto2_onset[301:400] - dat$chrome_plugin_opto1_onset[301:400]

firefox_plugin_20ms <- dat$firefox_plugin_opto2_onset[1:100] - dat$firefox_plugin_opto1_onset[1:100]
firefox_plugin_50ms <- dat$firefox_plugin_opto2_onset[101:200] - dat$firefox_plugin_opto1_onset[101:200]
firefox_plugin_150ms <- dat$firefox_plugin_opto2_onset[201:300] - dat$firefox_plugin_opto1_onset[201:300]
firefox_plugin_500ms <- dat$firefox_plugin_opto2_onset[301:400] - dat$firefox_plugin_opto1_onset[301:400]

edge_plugin_20ms <- dat$edge_plugin_opto2_onset[1:100] - dat$edge_plugin_opto1_onset[1:100]
edge_plugin_50ms <- dat$edge_plugin_opto2_onset[101:200] - dat$edge_plugin_opto1_onset[101:200]
edge_plugin_150ms <- dat$edge_plugin_opto2_onset[201:300] - dat$edge_plugin_opto1_onset[201:300]
edge_plugin_500ms <- dat$edge_plugin_opto2_onset[301:400] - dat$edge_plugin_opto1_onset[301:400] 

y_Max <- 100
chrome_color <- "#dc143c"
firefox_color <- "#006400"
edge_color <- "#1E90FF"
horiz_label <- "SOA (ms)"

```

### SOAs between the onset of the 150-ms square and the 20-ms square

The bin width is 5 ms in all histograms.

The scale of the horizontal axis is fixed for each condition.

## 20-ms SOA {.tabset}
###  No Plugin Chrome

Mean = `r round(mean(chrome_no_plugin_20ms, na.rm=T), 1)`

SD = `r round(sd(chrome_no_plugin_20ms, na.rm=T), 1)`

```{r}
hist(chrome_no_plugin_20ms, breaks=xRange_20ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### No Plugin Firefox

Mean = `r round(mean(firefox_no_plugin_20ms, na.rm=T), 1)`

SD = `r round(sd(firefox_no_plugin_20ms, na.rm=T), 1)`

```{r}
hist(firefox_no_plugin_20ms, breaks=xRange_20ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### No Plugin Edge

Mean = `r round(mean(edge_no_plugin_20ms, na.rm=T), 1)`

SD = `r round(sd(edge_no_plugin_20ms, na.rm=T), 1)`

```{r}
hist(edge_no_plugin_20ms, breaks=xRange_20ms, xlab=horiz_label, ylim=c(0, y_Max), col=edge_color)
```

###  Plugin Chrome

Mean = `r round(mean(chrome_plugin_20ms, na.rm=T), 1)`

SD = `r round(sd(chrome_plugin_20ms, na.rm=T), 1)`

```{r}
hist(chrome_plugin_20ms, breaks=xRange_20ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### Plugin Firefox

Mean = `r round(mean(firefox_plugin_20ms, na.rm=T), 1)`

SD = `r round(sd(firefox_plugin_20ms, na.rm=T), 1)`

```{r}
hist(firefox_plugin_20ms, breaks=xRange_20ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### Plugin Edge

Mean = `r round(mean(edge_plugin_20ms, na.rm=T), 1)`

SD = `r round(sd(edge_plugin_20ms, na.rm=T), 1)`

```{r}
hist(edge_plugin_20ms, breaks=xRange_20ms, xlab=horiz_label, ylim=c(0, y_Max), col=edge_color)
```

## 50-ms SOA {.tabset}
###  No Plugin Chrome

Mean = `r round(mean(chrome_no_plugin_50ms, na.rm=T), 1)`

SD = `r round(sd(chrome_no_plugin_50ms, na.rm=T), 1)`

```{r}
hist(chrome_no_plugin_50ms, breaks=xRange_50ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### No Plugin Firefox

Mean = `r round(mean(firefox_no_plugin_50ms, na.rm=T), 1)`

SD = `r round(sd(firefox_no_plugin_50ms, na.rm=T), 1)`

```{r}
hist(firefox_no_plugin_50ms, breaks=xRange_50ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### No Plugin Edge

Mean = `r round(mean(edge_no_plugin_50ms, na.rm=T), 1)`

SD = `r round(sd(edge_no_plugin_50ms, na.rm=T), 1)`

```{r}
hist(edge_no_plugin_50ms, breaks=xRange_50ms, xlab=horiz_label, ylim=c(0, y_Max), col=edge_color)
```

###  Plugin Chrome

Mean = `r round(mean(chrome_plugin_50ms, na.rm=T), 1)`

SD = `r round(sd(chrome_plugin_50ms, na.rm=T), 1)`

```{r}
hist(chrome_plugin_50ms, breaks=xRange_50ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### Plugin Firefox

Mean = `r round(mean(firefox_plugin_50ms, na.rm=T), 1)`

SD = `r round(sd(firefox_plugin_50ms, na.rm=T), 1)`

```{r}
hist(firefox_plugin_50ms, breaks=xRange_50ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### Plugin Edge

Mean = `r round(mean(edge_plugin_50ms, na.rm=T), 1)`

SD = `r round(sd(edge_plugin_50ms, na.rm=T), 1)`

```{r}
hist(edge_plugin_50ms, breaks=xRange_50ms, xlab=horiz_label, ylim=c(0, y_Max), col=edge_color)
```


## 150-ms SOA {.tabset}
###  No Plugin Chrome

Mean = `r round(mean(chrome_no_plugin_150ms, na.rm=T), 1)`

SD = `r round(sd(chrome_no_plugin_150ms, na.rm=T), 1)`

```{r}
hist(chrome_no_plugin_150ms, breaks=xRange_150ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### No Plugin Firefox

Mean = `r round(mean(firefox_no_plugin_150ms, na.rm=T), 1)`

SD = `r round(sd(firefox_no_plugin_150ms, na.rm=T), 1)`

```{r}
hist(firefox_no_plugin_150ms, breaks=xRange_150ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### No Plugin Edge

Mean = `r round(mean(edge_no_plugin_150ms, na.rm=T), 1)`

SD = `r round(sd(edge_no_plugin_150ms, na.rm=T), 1)`

```{r}
hist(edge_no_plugin_150ms, breaks=xRange_150ms, xlab=horiz_label, ylim=c(0, y_Max), col=edge_color)
```

###  Plugin Chrome

Mean = `r round(mean(chrome_plugin_150ms, na.rm=T), 1)`

SD = `r round(sd(chrome_plugin_150ms, na.rm=T), 1)`

```{r}
hist(chrome_plugin_150ms, breaks=xRange_150ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### Plugin Firefox

Mean = `r round(mean(firefox_plugin_150ms, na.rm=T), 1)`

SD = `r round(sd(firefox_plugin_150ms, na.rm=T), 1)`

```{r}
hist(firefox_plugin_150ms, breaks=xRange_150ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### Plugin Edge

Mean = `r round(mean(edge_plugin_150ms, na.rm=T), 1)`

SD = `r round(sd(edge_plugin_150ms, na.rm=T), 1)`

```{r}
hist(edge_plugin_150ms, breaks=xRange_150ms, xlab=horiz_label, ylim=c(0, y_Max), col=edge_color)
```


## 500-ms SOA {.tabset}
###  No Plugin Chrome

Mean = `r round(mean(chrome_no_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(chrome_no_plugin_500ms, na.rm=T), 1)`

```{r}
hist(chrome_no_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### No Plugin Firefox

Mean = `r round(mean(firefox_no_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(firefox_no_plugin_500ms, na.rm=T), 1)`

```{r}
hist(firefox_no_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### No Plugin Edge

Mean = `r round(mean(edge_no_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(edge_no_plugin_500ms, na.rm=T), 1)`

```{r}
hist(edge_no_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=edge_color)
```

###  Plugin Chrome

Mean = `r round(mean(chrome_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(chrome_plugin_500ms, na.rm=T), 1)`

```{r}
hist(chrome_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### Plugin Firefox

Mean = `r round(mean(firefox_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(firefox_plugin_500ms, na.rm=T), 1)`

```{r}
hist(firefox_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### Plugin Edge

Mean = `r round(mean(edge_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(edge_plugin_500ms, na.rm=T), 1)`

```{r}
hist(edge_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=edge_color)
```
