---
title: "MacBook Pro"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
device <- 3 # Change also the title of this script.
bin_width <- 5 # ms
if (device == 1){
  dat <- read.csv('Study2_ProBook.csv', header = F)
  xRange_visual <- seq(460, 600, bin_width)
  xRange_audio <- seq(80, 120, bin_width)
} else if (device == 2) {
  dat <- read.csv('Study2_OptiPlex.csv', header = F)
  xRange_visual <- seq(450, 650, bin_width)
  xRange_audio <- seq(80, 120, bin_width)
} else if (device == 3) {
  dat <- read.csv('Study2_MacBookPro.csv', header = F)
  xRange_visual <- seq(460, 540, bin_width)
  xRange_audio <- seq(80, 120, bin_width)
} else {
  dat <- read.csv('Study2_iMac.csv', header = F)
  xRange_visual <- seq(460, 540, bin_width)
  xRange_audio <- seq(60, 120, bin_width)
}

# "safari" is replaced by "safari" on the Mac
myColNames <- c(
	"chrome_opto1_onset", "chrome_opto1_offset", "chrome_opto1_duration",
	"chrome_mic1_onset", "chrome_mic1_offset", "chrome_mic1_duration",
	"firefox_opto1_onset", "firefox_opto1_offset", "firefox_opto1_duration",
	"firefox_mic1_onset", "firefox_mic1_offset", "firefox_mic1_duration",
	"safari_opto1_onset", "safari_opto1_offset", "safari_opto1_duration",
	"safari_mic1_onset", "safari_mic1_offset", "safari_mic1_duration")
colnames(dat) <- myColNames

##############
# No plugin
chrome_no_plugin_visual <- dat$chrome_opto1_duration[1:100]
chrome_no_plugin_audio <- dat$chrome_mic1_duration[1:100]

firefox_no_plugin_visual <- dat$firefox_opto1_duration[1:100]
firefox_no_plugin_audio <- dat$firefox_mic1_duration[1:100]

safari_no_plugin_visual <- dat$safari_opto1_duration[1:100]
safari_no_plugin_audio <- dat$safari_mic1_duration[1:100]

##############
# Plugin
chrome_plugin_visual <- dat$chrome_opto1_duration[501:600]
chrome_plugin_audio <- dat$chrome_mic1_duration[501:600]

firefox_plugin_visual <- dat$firefox_opto1_duration[501:600]
firefox_plugin_audio <- dat$firefox_mic1_duration[501:600]

safari_plugin_visual <- dat$safari_opto1_duration[501:600]
safari_plugin_audio <- dat$safari_mic1_duration[501:600]

y_Max <- 100
chrome_color <- "#dc143c"
firefox_color <- "#006400"
safari_color <- "#1E90FF"
horiz_label <- "Display duration (ms)"

```

### Display and sound duration
The bin width is 5 ms in all histograms.

The scale of the horizontal axis is fixed for each condition.

## 500-ms display duration {.tabset}
###  No Plugin Chrome

Mean = `r round(mean(chrome_no_plugin_visual, na.rm=T), 1)`

SD = `r round(sd(chrome_no_plugin_visual, na.rm=T), 1)`

```{r}
hist(chrome_no_plugin_visual, breaks=xRange_visual, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### No Plugin Firefox

Mean = `r round(mean(firefox_no_plugin_visual, na.rm=T), 1)`

SD = `r round(sd(firefox_no_plugin_visual, na.rm=T), 1)`

```{r}
hist(firefox_no_plugin_visual, breaks=xRange_visual, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### No Plugin safari

Mean = `r round(mean(safari_no_plugin_visual, na.rm=T), 1)`

SD = `r round(sd(safari_no_plugin_visual, na.rm=T), 1)`

```{r}
hist(safari_no_plugin_visual, breaks=xRange_visual, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```


###  Plugin Chrome

Mean = `r round(mean(chrome_plugin_visual, na.rm=T), 1)`

SD = `r round(sd(chrome_plugin_visual, na.rm=T), 1)`

```{r}
hist(chrome_plugin_visual, breaks=xRange_visual, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### Plugin Firefox

Mean = `r round(mean(firefox_plugin_visual, na.rm=T), 1)`

SD = `r round(sd(firefox_plugin_visual, na.rm=T), 1)`

```{r}
hist(firefox_plugin_visual, breaks=xRange_visual, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### Plugin safari

Mean = `r round(mean(safari_plugin_visual, na.rm=T), 1)`

SD = `r round(sd(safari_plugin_visual, na.rm=T), 1)`

```{r}
hist(safari_plugin_visual, breaks=xRange_visual, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```


## 100-ms sound duration {.tabset}
###  No Plugin Chrome

Mean = `r round(mean(chrome_no_plugin_audio, na.rm=T), 1)`

SD = `r round(sd(chrome_no_plugin_audio, na.rm=T), 1)`

```{r}
horiz_label <- "Sound duration (ms)"
hist(chrome_no_plugin_audio, breaks=xRange_audio, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### No Plugin Firefox

Mean = `r round(mean(firefox_no_plugin_audio, na.rm=T), 1)`

SD = `r round(sd(firefox_no_plugin_audio, na.rm=T), 1)`

```{r}
hist(firefox_no_plugin_audio, breaks=xRange_audio, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### No Plugin safari

Mean = `r round(mean(safari_no_plugin_audio, na.rm=T), 1)`

SD = `r round(sd(safari_no_plugin_audio, na.rm=T), 1)`

```{r}
hist(safari_no_plugin_audio, breaks=xRange_audio, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```

###  Plugin Chrome

Mean = `r round(mean(chrome_plugin_audio, na.rm=T), 1)`

SD = `r round(sd(chrome_plugin_audio, na.rm=T), 1)`

```{r}
hist(chrome_plugin_audio, breaks=xRange_audio, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### Plugin Firefox

Mean = `r round(mean(firefox_plugin_audio, na.rm=T), 1)`

SD = `r round(sd(firefox_plugin_audio, na.rm=T), 1)`

```{r}
hist(firefox_plugin_audio, breaks=xRange_audio, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### Plugin safari

Mean = `r round(mean(safari_plugin_audio, na.rm=T), 1)`

SD = `r round(sd(safari_plugin_audio, na.rm=T), 1)`

```{r}
hist(safari_plugin_audio, breaks=xRange_audio, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```

