---
title: "MacBook Pro"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
device <- 3 # Change also the title of this script.
bin_width <- 5 # ms
if (device == 1){
  dat <- read.csv('Study2_ProBook.csv', header = F)
  dat2 <- read.csv('Study2_ProBook_post_hoc.csv', header = F)
  xRange_0ms <- seq(-50, 150, bin_width)
  xRange_20ms <- seq(-20, 60, bin_width)
  xRange_50ms <- seq(0, 80, bin_width)
  xRange_150ms <- seq(100, 180, bin_width)
  xRange_500ms <- seq(460, 600, bin_width)
} else if (device == 2) {
  dat <- read.csv('Study2_OptiPlex.csv', header = F)
  dat2 <- read.csv('Study2_OptiPlex_post_hoc.csv', header = F)
  xRange_0ms <- seq(-60, 60, bin_width)
  xRange_20ms <- seq(-20, 60, bin_width)
  xRange_50ms <- seq(0, 80, bin_width)
  xRange_150ms <- seq(100, 180, bin_width)
  xRange_500ms <- seq(400, 650, bin_width)
} else if (device == 3) {
  dat <- read.csv('Study2_MacBookPro.csv', header = F)
  dat2 <- read.csv('Study2_MacBookPro_post_hoc.csv', header = F)
  xRange_0ms <- seq(-60, 0, bin_width)
  xRange_20ms <- seq(-40, 20, bin_width)
  xRange_50ms <- seq(-20, 60, bin_width)
  xRange_150ms <- seq(80, 140, bin_width)
  xRange_500ms <- seq(400, 700, bin_width)
} else {
  dat <- read.csv('Study2_iMac.csv', header = F)
  dat2 <- read.csv('Study2_iMac_post_hoc.csv', header = F)
  xRange_0ms <- seq(-80, 20, bin_width)
  xRange_20ms <- seq(-60, 40, bin_width)
  xRange_50ms <- seq(-40, 60, bin_width)
  xRange_150ms <- seq(60, 160, bin_width)
  xRange_500ms <- seq(400, 700, bin_width)
}

myColNames <- c(
	"chrome_opto1_onset", "chrome_opto1_offset", "chrome_opto1_duration",
	"chrome_mic1_onset", "chrome_mic1_offset", "chrome_mic1_duration",
	"firefox_opto1_onset", "firefox_opto1_offset", "firefox_opto1_duration",
	"firefox_mic1_onset", "firefox_mic1_offset", "firefox_mic1_duration",
	"safari_opto1_onset", "safari_opto1_offset", "safari_opto1_duration",
	"safari_mic1_onset", "safari_mic1_offset", "safari_mic1_duration")
colnames(dat) <- myColNames
colnames(dat2) <- myColNames

##############
# No plugin
chrome_no_plugin_0ms <- dat2$chrome_mic1_onset[1:100] - dat2$chrome_opto1_onset[1:100]
chrome_no_plugin_500ms <- dat$chrome_mic1_onset[1:100] - dat$chrome_opto1_onset[1:100]

firefox_no_plugin_0ms <- dat2$firefox_mic1_onset[1:100] - dat2$firefox_opto1_onset[1:100]
firefox_no_plugin_500ms <- dat$firefox_mic1_onset[1:100] - dat$firefox_opto1_onset[1:100]

safari_no_plugin_0ms <- dat2$safari_mic1_onset[1:100] - dat2$safari_opto1_onset[1:100]
safari_no_plugin_500ms <- dat$safari_mic1_onset[1:100] - dat$safari_opto1_onset[1:100]

##############
# Plugin
chrome_plugin_0ms <- dat$chrome_mic1_onset[101:200] - dat$chrome_opto1_onset[101:200]
chrome_plugin_20ms <- dat$chrome_mic1_onset[201:300] - dat$chrome_opto1_onset[201:300]
chrome_plugin_50ms <- dat$chrome_mic1_onset[301:400] - dat$chrome_opto1_onset[301:400]
chrome_plugin_150ms <- dat$chrome_mic1_onset[401:500] - dat$chrome_opto1_onset[401:500]
chrome_plugin_500ms <- dat$chrome_mic1_onset[501:600] - dat$chrome_opto1_onset[501:600]

firefox_plugin_0ms <- dat$firefox_mic1_onset[101:200] - dat$firefox_opto1_onset[101:200]
firefox_plugin_20ms <- dat$firefox_mic1_onset[201:300] - dat$firefox_opto1_onset[201:300]
firefox_plugin_50ms <- dat$firefox_mic1_onset[301:400] - dat$firefox_opto1_onset[301:400]
firefox_plugin_150ms <- dat$firefox_mic1_onset[401:500] - dat$firefox_opto1_onset[401:500]
firefox_plugin_500ms <- dat$firefox_mic1_onset[501:600] - dat$firefox_opto1_onset[501:600]

safari_plugin_0ms <- dat$safari_mic1_onset[101:200] - dat$safari_opto1_onset[101:200]
safari_plugin_20ms <- dat$safari_mic1_onset[201:300] - dat$safari_opto1_onset[201:300]
safari_plugin_50ms <- dat$safari_mic1_onset[301:400] - dat$safari_opto1_onset[301:400]
safari_plugin_150ms <- dat$safari_mic1_onset[401:500] - dat$safari_opto1_onset[401:500]
safari_plugin_500ms <- dat$safari_mic1_onset[501:600] - dat$safari_opto1_onset[501:600]

y_Max <- 60
chrome_color <- "#dc143c"
firefox_color <- "#006400"
safari_color <- "#1E90FF"
horiz_label <- "SOA (ms)"

```

### SOA between square and sound
The bin width is 5 ms in all histograms.

The scale of the horizontal axis is fixed for each condition.


## 0-ms SOA {.tabset}

<!--

###  No Plugin Chrome

Mean = `r round(mean(chrome_no_plugin_0ms, na.rm=T), 1)`

SD = `r round(sd(chrome_no_plugin_0ms, na.rm=T), 1)`

```{r}
hist(chrome_no_plugin_0ms, breaks=xRange_0ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

###  No Plugin Firefox

Mean = `r round(mean(firefox_no_plugin_0ms, na.rm=T), 1)`

SD = `r round(sd(firefox_no_plugin_0ms, na.rm=T), 1)`

```{r}
hist(firefox_no_plugin_0ms, breaks=xRange_0ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

###  No Plugin Safari

Mean = `r round(mean(safari_no_plugin_0ms, na.rm=T), 1)`

SD = `r round(sd(safari_no_plugin_0ms, na.rm=T), 1)`

```{r}
hist(safari_no_plugin_0ms, breaks=xRange_0ms, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```

-->

###  Plugin Chrome

Mean = `r round(mean(chrome_plugin_0ms, na.rm=T), 1)`

SD = `r round(sd(chrome_plugin_0ms, na.rm=T), 1)`

```{r}
hist(chrome_plugin_0ms, breaks=xRange_0ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

###  Plugin Firefox

Mean = `r round(mean(firefox_plugin_0ms, na.rm=T), 1)`

SD = `r round(sd(firefox_plugin_0ms, na.rm=T), 1)`

```{r}
hist(firefox_plugin_0ms, breaks=xRange_0ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

###  Plugin Safari

Mean = `r round(mean(safari_plugin_0ms, na.rm=T), 1)`

SD = `r round(sd(safari_plugin_0ms, na.rm=T), 1)`

```{r}
hist(safari_plugin_0ms, breaks=xRange_0ms, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```

## 20-ms SOA {.tabset}
###  Plugin Chrome

Mean = `r round(mean(chrome_plugin_20ms, na.rm=T), 1)`

SD = `r round(sd(chrome_plugin_20ms, na.rm=T), 1)`

```{r}
hist(chrome_plugin_20ms, breaks=xRange_20ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

###  Plugin Firefox

Mean = `r round(mean(firefox_plugin_20ms, na.rm=T), 1)`

SD = `r round(sd(firefox_plugin_20ms, na.rm=T), 1)`

```{r}
hist(firefox_plugin_20ms, breaks=xRange_20ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

###  Plugin Safari

Mean = `r round(mean(safari_plugin_20ms, na.rm=T), 1)`

SD = `r round(sd(safari_plugin_20ms, na.rm=T), 1)`

```{r}
hist(safari_plugin_20ms, breaks=xRange_20ms, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```

## 50-ms SOA {.tabset}
###  Plugin Chrome

Mean = `r round(mean(chrome_plugin_50ms, na.rm=T), 1)`

SD = `r round(sd(chrome_plugin_50ms, na.rm=T), 1)`

```{r}
hist(chrome_plugin_50ms, breaks=xRange_50ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

###  Plugin Firefox

Mean = `r round(mean(firefox_plugin_50ms, na.rm=T), 1)`

SD = `r round(sd(firefox_plugin_50ms, na.rm=T), 1)`

```{r}
hist(firefox_plugin_50ms, breaks=xRange_50ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

###  Plugin Safari

Mean = `r round(mean(safari_plugin_50ms, na.rm=T), 1)`

SD = `r round(sd(safari_plugin_50ms, na.rm=T), 1)`

```{r}
hist(safari_plugin_50ms, breaks=xRange_50ms, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```

## 150-ms SOA {.tabset}
###  Plugin Chrome

Mean = `r round(mean(chrome_plugin_150ms, na.rm=T), 1)`

SD = `r round(sd(chrome_plugin_150ms, na.rm=T), 1)`

```{r}
hist(chrome_plugin_150ms, breaks=xRange_150ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

###  Plugin Firefox

Mean = `r round(mean(firefox_plugin_150ms, na.rm=T), 1)`

SD = `r round(sd(firefox_plugin_150ms, na.rm=T), 1)`

```{r}
hist(firefox_plugin_150ms, breaks=xRange_150ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

###  Plugin Safari

Mean = `r round(mean(safari_plugin_150ms, na.rm=T), 1)`

SD = `r round(sd(safari_plugin_150ms, na.rm=T), 1)`

```{r}
hist(safari_plugin_150ms, breaks=xRange_150ms, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```

## 500-ms SOA {.tabset}
###  No Plugin Chrome

Mean = `r round(mean(chrome_no_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(chrome_no_plugin_500ms, na.rm=T), 1)`

```{r}
hist(chrome_no_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

###  No Plugin Firefox

Mean = `r round(mean(firefox_no_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(firefox_no_plugin_500ms, na.rm=T), 1)`

```{r}
hist(firefox_no_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

###  No Plugin Safari

Mean = `r round(mean(safari_no_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(safari_no_plugin_500ms, na.rm=T), 1)`

```{r}
hist(safari_no_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```

###  Plugin Chrome

Mean = `r round(mean(chrome_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(chrome_plugin_500ms, na.rm=T), 1)`

```{r}
hist(chrome_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

###  Plugin Firefox

Mean = `r round(mean(firefox_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(firefox_plugin_500ms, na.rm=T), 1)`

```{r}
hist(firefox_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

###  Plugin Safari

Mean = `r round(mean(safari_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(safari_plugin_500ms, na.rm=T), 1)`

```{r}
hist(safari_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```


