---
title: "iMac"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
device <- 4 # Change also the title of this script.
bin_width <- 5 # ms
if (device == 1){
  dat <- read.csv('Study1_ProBook.csv', header = F)
  xRange_20ms <- seq(0, 80, bin_width)
  xRange_50ms <- seq(0, 140, bin_width)
  xRange_150ms <- seq(120, 260, bin_width)
  xRange_500ms <- seq(460, 600, bin_width)
} else if (device == 2) {
  dat <- read.csv('Study1_OptiPlex.csv', header = F)
  xRange_20ms <- seq(20, 100, bin_width)
  xRange_50ms <- seq(20, 120, bin_width)
  xRange_150ms <- seq(120, 220, bin_width)
  xRange_500ms <- seq(460, 560, bin_width)
} else if (device == 3) {
  dat <- read.csv('Study1_MacBookPro.csv', header = F)
  xRange_20ms <- seq(0, 80, bin_width)
  xRange_50ms <- seq(20, 100, bin_width)
  xRange_150ms <- seq(120, 200, bin_width)
  xRange_500ms <- seq(460, 560, bin_width)
} else {
  dat <- read.csv('Study1_iMac.csv', header = F)
  xRange_20ms <- seq(0, 80, bin_width)
  xRange_50ms <- seq(20, 100, bin_width)
  xRange_150ms <- seq(120, 200, bin_width)
  xRange_500ms <- seq(480, 560, bin_width)
}

myColNames <- c(
	"chrome_no_plugin_opto2_onset", "chrome_no_plugin_opto2_offset", "chrome_no_plugin_opto2_duration",
	"chrome_no_plugin_opto1_onset", "chrome_no_plugin_opto1_offset", "chrome_no_plugin_opto1_duration",
	"chrome_plugin_opto2_onset", "chrome_plugin_opto2_offset", "chrome_plugin_opto2_duration",
	"chrome_plugin_opto1_onset", "chrome_plugin_opto1_offset", "chrome_plugin_opto1_duration",
	"firefox_no_plugin_opto2_onset", "firefox_no_plugin_opto2_offset", "firefox_no_plugin_opto2_duration",
	"firefox_no_plugin_opto1_onset", "firefox_no_plugin_opto1_offset", "firefox_no_plugin_opto1_duration",
	"firefox_plugin_opto2_onset", "firefox_plugin_opto2_offset", "firefox_plugin_opto2_duration",
	"firefox_plugin_opto1_onset", "firefox_plugin_opto1_offset", "firefox_plugin_opto1_duration",
	"safari_no_plugin_opto2_onset", "safari_no_plugin_opto2_offset", "safari_no_plugin_opto2_duration",
	"safari_no_plugin_opto1_onset", "safari_no_plugin_opto1_offset", "safari_no_plugin_opto1_duration",
	"safari_plugin_opto2_onset", "safari_plugin_opto2_offset", "safari_plugin_opto2_duration",
	"safari_plugin_opto1_onset", "safari_plugin_opto1_offset", "safari_plugin_opto1_duration")
colnames(dat) <- myColNames

##############
# No plugin
chrome_no_plugin_20ms <- dat$chrome_no_plugin_opto2_onset[401:500] - dat$chrome_no_plugin_opto1_onset[401:500]
chrome_no_plugin_50ms <- dat$chrome_no_plugin_opto2_onset[501:600] - dat$chrome_no_plugin_opto1_onset[501:600]
chrome_no_plugin_150ms <- dat$chrome_no_plugin_opto2_onset[601:700] - dat$chrome_no_plugin_opto1_onset[601:700]
chrome_no_plugin_500ms <- dat$chrome_no_plugin_opto2_onset[701:800] - dat$chrome_no_plugin_opto1_onset[701:800]

firefox_no_plugin_20ms <- dat$firefox_no_plugin_opto2_onset[401:500] - dat$firefox_no_plugin_opto1_onset[401:500]
firefox_no_plugin_50ms <- dat$firefox_no_plugin_opto2_onset[501:600] - dat$firefox_no_plugin_opto1_onset[501:600]
firefox_no_plugin_150ms <- dat$firefox_no_plugin_opto2_onset[601:700] - dat$firefox_no_plugin_opto1_onset[601:700]
firefox_no_plugin_500ms <- dat$firefox_no_plugin_opto2_onset[701:800] - dat$firefox_no_plugin_opto1_onset[701:800]

safari_no_plugin_20ms <- dat$safari_no_plugin_opto2_onset[401:500] - dat$safari_no_plugin_opto1_onset[401:500]
safari_no_plugin_50ms <- dat$safari_no_plugin_opto2_onset[501:600] - dat$safari_no_plugin_opto1_onset[501:600]
safari_no_plugin_150ms <- dat$safari_no_plugin_opto2_onset[601:700] - dat$safari_no_plugin_opto1_onset[601:700]
safari_no_plugin_500ms <- dat$safari_no_plugin_opto2_onset[701:800] - dat$safari_no_plugin_opto1_onset[701:800]

##############
# Plugin
chrome_plugin_20ms <- dat$chrome_plugin_opto2_onset[401:500] - dat$chrome_plugin_opto1_onset[401:500]
chrome_plugin_50ms <- dat$chrome_plugin_opto2_onset[501:600] - dat$chrome_plugin_opto1_onset[501:600]
chrome_plugin_150ms <- dat$chrome_plugin_opto2_onset[601:700] - dat$chrome_plugin_opto1_onset[601:700]
chrome_plugin_500ms <- dat$chrome_plugin_opto2_onset[701:800] - dat$chrome_plugin_opto1_onset[701:800]

firefox_plugin_20ms <- dat$firefox_plugin_opto2_onset[401:500] - dat$firefox_plugin_opto1_onset[401:500]
firefox_plugin_50ms <- dat$firefox_plugin_opto2_onset[501:600] - dat$firefox_plugin_opto1_onset[501:600]
firefox_plugin_150ms <- dat$firefox_plugin_opto2_onset[601:700] - dat$firefox_plugin_opto1_onset[601:700]
firefox_plugin_500ms <- dat$firefox_plugin_opto2_onset[701:800] - dat$firefox_plugin_opto1_onset[701:800]

safari_plugin_20ms <- dat$safari_plugin_opto2_onset[401:500] - dat$safari_plugin_opto1_onset[401:500]
safari_plugin_50ms <- dat$safari_plugin_opto2_onset[501:600] - dat$safari_plugin_opto1_onset[501:600]
safari_plugin_150ms <- dat$safari_plugin_opto2_onset[601:700] - dat$safari_plugin_opto1_onset[601:700]
safari_plugin_500ms <- dat$safari_plugin_opto2_onset[701:800] - dat$safari_plugin_opto1_onset[701:800] 

y_Max <- 100
chrome_color <- "#dc143c"
firefox_color <- "#006400"
safari_color <- "#1E90FF"
horiz_label <- "SOA (ms)"

```

### SOAs between the onset of the 500-ms square and the 50-ms square

The bin width is 5 ms in all histograms.

The scale of the horizontal axis is fixed for each condition.

## 20-ms SOA {.tabset}
###  No Plugin Chrome

Mean = `r round(mean(chrome_no_plugin_20ms, na.rm=T), 1)`

SD = `r round(sd(chrome_no_plugin_20ms, na.rm=T), 1)`

```{r}
hist(chrome_no_plugin_20ms, breaks=xRange_20ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### No Plugin Firefox

Mean = `r round(mean(firefox_no_plugin_20ms, na.rm=T), 1)`

SD = `r round(sd(firefox_no_plugin_20ms, na.rm=T), 1)`

```{r}
hist(firefox_no_plugin_20ms, breaks=xRange_20ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### No Plugin Safari

Mean = `r round(mean(safari_no_plugin_20ms, na.rm=T), 1)`

SD = `r round(sd(safari_no_plugin_20ms, na.rm=T), 1)`

```{r}
hist(safari_no_plugin_20ms, breaks=xRange_20ms, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```

###  Plugin Chrome

Mean = `r round(mean(chrome_plugin_20ms, na.rm=T), 1)`

SD = `r round(sd(chrome_plugin_20ms, na.rm=T), 1)`

```{r}
hist(chrome_plugin_20ms, breaks=xRange_20ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### Plugin Firefox

Mean = `r round(mean(firefox_plugin_20ms, na.rm=T), 1)`

SD = `r round(sd(firefox_plugin_20ms, na.rm=T), 1)`

```{r}
hist(firefox_plugin_20ms, breaks=xRange_20ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### Plugin Safari

Mean = `r round(mean(safari_plugin_20ms, na.rm=T), 1)`

SD = `r round(sd(safari_plugin_20ms, na.rm=T), 1)`

```{r}
hist(safari_plugin_20ms, breaks=xRange_20ms, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```

## 50-ms SOA {.tabset}
###  No Plugin Chrome

Mean = `r round(mean(chrome_no_plugin_50ms, na.rm=T), 1)`

SD = `r round(sd(chrome_no_plugin_50ms, na.rm=T), 1)`

```{r}
hist(chrome_no_plugin_50ms, breaks=xRange_50ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### No Plugin Firefox

Mean = `r round(mean(firefox_no_plugin_50ms, na.rm=T), 1)`

SD = `r round(sd(firefox_no_plugin_50ms, na.rm=T), 1)`

```{r}
hist(firefox_no_plugin_50ms, breaks=xRange_50ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### No Plugin Safari

Mean = `r round(mean(safari_no_plugin_50ms, na.rm=T), 1)`

SD = `r round(sd(safari_no_plugin_50ms, na.rm=T), 1)`

```{r}
hist(safari_no_plugin_50ms, breaks=xRange_50ms, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```

###  Plugin Chrome

Mean = `r round(mean(chrome_plugin_50ms, na.rm=T), 1)`

SD = `r round(sd(chrome_plugin_50ms, na.rm=T), 1)`

```{r}
hist(chrome_plugin_50ms, breaks=xRange_50ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### Plugin Firefox

Mean = `r round(mean(firefox_plugin_50ms, na.rm=T), 1)`

SD = `r round(sd(firefox_plugin_50ms, na.rm=T), 1)`

```{r}
hist(firefox_plugin_50ms, breaks=xRange_50ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### Plugin Safari

Mean = `r round(mean(safari_plugin_50ms, na.rm=T), 1)`

SD = `r round(sd(safari_plugin_50ms, na.rm=T), 1)`

```{r}
hist(safari_plugin_50ms, breaks=xRange_50ms, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```


## 150-ms SOA {.tabset}
###  No Plugin Chrome

Mean = `r round(mean(chrome_no_plugin_150ms, na.rm=T), 1)`

SD = `r round(sd(chrome_no_plugin_150ms, na.rm=T), 1)`

```{r}
hist(chrome_no_plugin_150ms, breaks=xRange_150ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### No Plugin Firefox

Mean = `r round(mean(firefox_no_plugin_150ms, na.rm=T), 1)`

SD = `r round(sd(firefox_no_plugin_150ms, na.rm=T), 1)`

```{r}
hist(firefox_no_plugin_150ms, breaks=xRange_150ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### No Plugin Safari

Mean = `r round(mean(safari_no_plugin_150ms, na.rm=T), 1)`

SD = `r round(sd(safari_no_plugin_150ms, na.rm=T), 1)`

```{r}
hist(safari_no_plugin_150ms, breaks=xRange_150ms, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```

###  Plugin Chrome

Mean = `r round(mean(chrome_plugin_150ms, na.rm=T), 1)`

SD = `r round(sd(chrome_plugin_150ms, na.rm=T), 1)`

```{r}
hist(chrome_plugin_150ms, breaks=xRange_150ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### Plugin Firefox

Mean = `r round(mean(firefox_plugin_150ms, na.rm=T), 1)`

SD = `r round(sd(firefox_plugin_150ms, na.rm=T), 1)`

```{r}
hist(firefox_plugin_150ms, breaks=xRange_150ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### Plugin Safari

Mean = `r round(mean(safari_plugin_150ms, na.rm=T), 1)`

SD = `r round(sd(safari_plugin_150ms, na.rm=T), 1)`

```{r}
hist(safari_plugin_150ms, breaks=xRange_150ms, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```


## 500-ms SOA {.tabset}
###  No Plugin Chrome

Mean = `r round(mean(chrome_no_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(chrome_no_plugin_500ms, na.rm=T), 1)`

```{r}
hist(chrome_no_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### No Plugin Firefox

Mean = `r round(mean(firefox_no_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(firefox_no_plugin_500ms, na.rm=T), 1)`

```{r}
hist(firefox_no_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### No Plugin Safari

Mean = `r round(mean(safari_no_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(safari_no_plugin_500ms, na.rm=T), 1)`

```{r}
hist(safari_no_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```

###  Plugin Chrome

Mean = `r round(mean(chrome_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(chrome_plugin_500ms, na.rm=T), 1)`

```{r}
hist(chrome_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=chrome_color)
```

### Plugin Firefox

Mean = `r round(mean(firefox_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(firefox_plugin_500ms, na.rm=T), 1)`

```{r}
hist(firefox_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=firefox_color)
```

### Plugin Safari

Mean = `r round(mean(safari_plugin_500ms, na.rm=T), 1)`

SD = `r round(sd(safari_plugin_500ms, na.rm=T), 1)`

```{r}
hist(safari_plugin_500ms, breaks=xRange_500ms, xlab=horiz_label, ylim=c(0, y_Max), col=safari_color)
```
