---
title: "5-17 Markdown"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r data, include=FALSE}
startup <- function() {
  renv::isolate()
  packages <- c('tidyverse', 'Cairo', 'dqrng', 'readr','ggplot2')
  
  installed_packages <- packages %in% rownames(installed.packages())
  if (any(installed_packages == FALSE)) {
    install.packages(packages[!installed_packages])
  }
  invisible(lapply(packages, library, character.only = TRUE))
  rm(packages, installed_packages)
}

startup()
rm(list = ls())
data <- read_csv(
  "22-5-4 to 22-5-4 Data.csv",
  col_types = cols(
    trialNum = col_integer(),
    rt = col_double(),
    correct = col_logical(),
    winner = col_integer(),
    p1conf = col_integer(),
    p2conf = col_integer(),
    p1rslt = col_integer(),
    p2rslt = col_integer(),
    ...11 = col_skip()
  )
) %>%
  mutate(correct = as.integer(correct))


data <- bind_rows(
  filter(data, cntBalance == 'L') %>%
    mutate(
      hiConf = p1conf,
      loConf = p2conf,
      hiRslt = p1rslt,
      loRslt = p2rslt
    ) %>%
    select(-c(7:10)),
  filter(data, cntBalance == 'R') %>%
    mutate(
      hiConf = p2conf,
      loConf = p1conf,
      hiRslt = p2rslt,
      loRslt = p1rslt
    ) %>%
    select(-c(7:10))
)

```

Original data output by experiment.
Correct: Participant made the correct (1) prediction or wrong (0) prediction 
winner: which horse won (1 or 2)
hi/lo: high-calibrated vs low-calibrated advisor
Conf: high confidence prediction (1) vs low confidence prediction (0)
Rslt: advisor made the correct (1) prediction or wrong (0) prediction

```{r show data, echo=FALSE}
data
```

Plots of advisor confidence over 500 trials for four sample participants


```{r plot advisor accuracy, echo=FALSE}
#====
#Plot Advisor Accuracy

plotAdvisorAcc <- function(subject) {
  dataLonly <- filter(data, subID == subject)
  
  varName = c('_loConf', '_hiConf')
  for (i in 0:1) {
    assign(
      paste0('hiCal', varName[i + 1]),
      filter(dataLonly, hiConf == i) %>%
        mutate(
          winSum = cumsum(hiRslt),
          proportion = winSum / 1:length(winSum),
          group = paste0('hiCal', varName[i + 1])
        ),
      envir = globalenv()
    )
    
    assign(
      paste0('loCal', varName[i + 1]),
      filter(dataLonly, loConf == i) %>%
        mutate(
          winSum = cumsum(loRslt),
          proportion = winSum / 1:length(winSum),
          group = paste0('loCal', varName[i + 1])
        ),
      envir = globalenv()
    )
  }
  
  graphData <- bind_rows(hiCal_hiConf,
                         hiCal_loConf,
                         loCal_hiConf,
                         loCal_loConf) %>%
    arrange(group) %>%
    select(trialNum, proportion, group)
  
  ggplot(graphData,
         aes(
           x = trialNum,
           y = proportion,
           group = group,
           color = group
         )) +
    scale_color_manual(
      values = c(
        hiCal_hiConf = 'red',
        hiCal_loConf = 'blue',
        loCal_hiConf = 'orange',
        loCal_loConf = 'green'
      ),
      name = 'Advisors',
      labels = c(
        'Calibrated High Confidence',
        'Calibrated Low Confidence',
        'Non-Calibrated High Confidence',
        'Non-Calibrated Low Confidence'
      )
    ) +
    labs(title = "Advisor Accuracy by Confidence",
         x = "Trial Number", y = "Proportion Correct") +
    coord_cartesian(ylim = c(0, 1)) +
    #coord_cartesian(xlim = c(0, 500)) +
    geom_step()
}

plotAdvisorAcc('0uk')
plotAdvisorAcc('aya')
plotAdvisorAcc('pj7')
plotAdvisorAcc('ynb')
```

```{r plot sign test, include=FALSE}
totalsTable <- mutate(data,
                      advAgree = ifelse(hiRslt == loRslt, 1, 0),) %>%
  filter(advAgree == 0) %>%
  group_by(subID) %>%
  summarise(
    disagree = sum(advAgree != ''),
    HH = sum(hiConf == 1 & loConf == 1),
    HL = sum(hiConf == 1 & loConf == 0),
    LL = sum(hiConf == 0 & loConf == 0),
    LH = sum(hiConf == 0 & loConf == 1),
    
    H_HH = sum(hiConf == 1 &
                 loConf == 1 &
                 correct == hiRslt) / HH,
    H_HL = sum(hiConf == 1 &
                 loConf == 0 &
                 correct == hiRslt) / HL,
    H_LH = sum(hiConf == 0 &
                 loConf == 1 &
                 correct == hiRslt) / LH,
    H_LL = sum(hiConf == 0 &
                 loConf == 0 &
                 correct == hiRslt) / LL,
  )

signTestData <- summarise(
  totalsTable,
  Hcnt_HH = sum(H_HH > .5),
  Hcnt_HL = sum(H_HL > .5),
  Hcnt_LH = sum(H_LH > .5),
  Hcnt_LL = sum(H_LL > .5),
  
  Ncnt_HH = sum(H_HH == .5),
  Ncnt_HL = sum(H_HL == .5),
  Ncnt_LH = sum(H_LH == .5),
  Ncnt_LL = sum(H_LL == .5),
  
  Lcnt_HH = sum(H_HH < .5),
  Lcnt_HL = sum(H_HL < .5),
  Lcnt_LH = sum(H_LH < .5),
  Lcnt_LL = sum(H_LL < .5),
) %>%
  pivot_longer(
    cols = c(
      'Hcnt_HH',
      'Hcnt_HL',
      'Hcnt_LH',
      'Hcnt_LL',
      'Ncnt_HH',
      'Ncnt_HL',
      'Ncnt_LH',
      'Ncnt_LL',
      'Lcnt_HH',
      'Lcnt_HL',
      'Lcnt_LH',
      'Lcnt_LL',
    )
  ) %>%
  mutate(one = c(rep('High', 4), rep('None', 4), rep('Low', 4)),
         two = rep(c(
           'High vs High', 'High vs Low', 'Low vs High', 'Low vs Low'
         ), 3)) %>%
  select(-1)

```

Tables & Plots for participant agreement with advisors
Table 1. Proportion of trials which each participant agreed with one of the two advisors when
both advisors gave different responses (disagree)
Table 2. Number of participants that agreed with one of the two advisors for the majority (<.5) of trials
Figure 1. Boxplot of agreement data
```{r test, echo=FALSE}
totalsTable
signTestData
ggplot(signTestData, aes(
  fill = factor(one, levels = c('Low', 'None', 'High')),
  y = value,
  x = two
)) +
  geom_bar(position = "stack", stat = "identity") +
  scale_y_continuous(breaks = c(0, 9 / 2, 9)) +
  scale_fill_manual(
    values = c(Low = 'lightblue',
               None = 'ivory4',
               High = 'lightblue4'),
    name = 'Advisor Followed',
    labels = c(
      'Non-Calibrated Advisor',
      'Neither Advisor',
      'High-Calibrated Advisor'
    )
  ) +
  labs(title = "Agreement with Well/Non-calibrated Advisor",
       x = "Advisor (High-Calibrated vs Non-Calibrated) Confidence", y = "# of times ")
```
